Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-24 paper/main.tex
minor updates

\begin{table}
\begin{tabular}{lllll}
Author & Web Method & Halo Finder & Major Axis & Correlation\\
\end{tabular}
SHAPE
\end{table}

>>>>

A novel aspect of our study is the use of a
single computational volume of a high resolution simulation to study
the alignments. Equally important, is our focus to quantify to what
extent  these results depend on the method used to define the cosmic
web and the numerical choices to implement the algorithms.
